Supplementary Material for the article \textit{Quotient Normalized Maximum Likelihood Criterion for Learning Bayesian Network Structures}

### 2017-10-13 experiments.tex
Added a comment about BDq to supp mat.

The graphs for different sample sizes for both predictive accuracy and
the number of parameters can be found in Appendix D in the Supplementary Material.

>>>>

The graphs for different sample sizes for both predictive accuracy and
the number of parameters can be found in Appendix E in the Supplementary Material.
